Liveness-Based Garbage Collection for Lazy Languages

### 2016-04-16 paper/cfg-to-nfa.tex
some rewriting

We circumvent the problem of  undecidability by over approximating the
CFG by non-deterministic finite state automata (NFA) using
Mohri   and   Nederhof~\cite{mohri00regular}   method.   This   method
transforms a CFG $G$ into a strongly  regular grammar $R$ such that $\lang{G} \subseteq \lang{R}$. 
%%
If a CFG consists of a set of mutually recursive non-terminals such that the rules involved are not all left regular or not all right regular, then the method breaks the rules into right regular rules by introducing fresh non-terminals. For our example, the rule  $\var{\Df{\length}{1}}$ has two non regular productions,           $\acdr\var{\Df{\length}{1}}\clazy$          and
$\clazy\var{\Df{\length}{1}}{\clazy}$.  The steps for transforming these productions into
right regular productions are:

\begin{enumerate}
\item
Add a  new non-terminal  $\varnew{\Df{\length}{1}}$ to the  grammar with
the rule $\varnew{\Df{\length}{1}} \rightarrow \epsilon$.
\item
 Replace     $\var{\Df{\length}{1}}     \rightarrow     \clazy$,     by
 $\var{\Df{\length}{1}} \rightarrow \clazy\varnew{\Df{\length}{1}}$
\item
 Replace
 $\var{\Df{\length}{1}} \rightarrow \clazy\var{\Df{\length}{1}}\clazy$,
 by  $\var{\Df{\length}{1}}  \rightarrow  \clazy\var{\Df{\length}{1}}$
 and $\varnew{\Df{\length}{1}} \rightarrow \clazy\varnew{\Df{\length}{1}}$
\item
  Replace
 $\var{\Df{\length}{1}} \rightarrow \acdr\var{\Df{\length}{1}}\clazy$,
 by $\var{\Df{\length}{1}} \rightarrow \acdr\var{\Df{\length}{1}}$ and
 $\varnew{\Df{\length}{1}} \rightarrow \clazy\varnew{\Df{\length}{1}}$
\end{enumerate}

>>>>

We circumvent the problem of  undecidability by over approximating the
CFG by non-deterministic finite state automata (NFA) using
Mohri   and   Nederhof method~\cite{mohri00regular}.   This   method
transforms a CFG $G$ into a strongly  regular grammar $R$ such that $\lang{G} \subseteq \lang{R}$. 
%%
If a CFG consists of a set of mutually recursive non-terminals such that the rules involved are not all left regular or not all right regular, then the method breaks the rules into right regular rules by introducing fresh non-terminals. For our example, the rule  $\var{\Df{\length}{1}}$ has two non regular productions,           $\acdr\var{\Df{\length}{1}}\clazy$          and
$\clazy\var{\Df{\length}{1}}{\clazy}$.  The steps for transforming these productions into
right regular productions are:

\begin{enumerate}
\item
Add a  new non-terminal  $\varnew{\Df{\length}{1}}$ to the  grammar with
the rule $\varnew{\Df{\length}{1}} \rightarrow \epsilon$.
\item
 Replace     $\var{\Df{\length}{1}}     \rightarrow     \clazy$     by
 $\var{\Df{\length}{1}} \rightarrow \clazy\varnew{\Df{\length}{1}}$
\item
 Replace
 $\var{\Df{\length}{1}} \rightarrow \clazy\var{\Df{\length}{1}}\clazy$
 by  $\var{\Df{\length}{1}}  \rightarrow  \clazy\var{\Df{\length}{1}}$
 and \linebreak $\varnew{\Df{\length}{1}} \rightarrow \clazy\varnew{\Df{\length}{1}}$
\item
  Replace
 $\var{\Df{\length}{1}} \rightarrow \acdr\var{\Df{\length}{1}}\clazy$
 by $\var{\Df{\length}{1}} \rightarrow \acdr\var{\Df{\length}{1}}$ and
 \linebreak $\varnew{\Df{\length}{1}} \rightarrow \clazy\varnew{\Df{\length}{1}}$
\end{enumerate}
